The transition redshift as a probe of reionization

### 2019-08-13 paper/ms.tex
Line indent fix
Add some more commands
Add aveTb plot to paper

\newcommand{\avg}[1]{\ensuremath{\langle #1 \rangle}}
\newcommand{\CII}{\ensuremath{\text{C~\textsc{ii}}}}
\newcommand{\HII}{\ensuremath{\text{H~\textsc{ii}}}}
\newcommand{\OIII}{\ensuremath{\text{O~\textsc{iii}}}}

\newcommand{\Msun}{\ensuremath{\text{M}_\odot}}
\newcommand{\kpc}{\ensuremath{\text{kpc}}}
\newcommand{\Mpc}{\ensuremath{\text{Mpc}}}
\newcommand{\Myr}{\ensuremath{\text{Myr}}}
\newcommand{\Gyr}{\ensuremath{\text{Gyr}}}
\newcommand{\kms}{\ensuremath{\text{km}\,\text{s}^{-1}}}

@@

\newcommand{\zst}{\ensuremath{z_{\star}}}

@@

\section{Results} \label{sec:results}
\subsection{The halo field}
{\bf If we switch to LIM I think this section should be scrapped, except
showing ztran vs k but using LIM and density instead of halos}

>>>>

\newcommand{\avg}[1]{\ensuremath{\langle #1 \rangle}}
\newcommand{\CII}{\ensuremath{\text{C~\textsc{ii}}}}
\newcommand{\HII}{\ensuremath{\text{H~\textsc{ii}}}}
\newcommand{\OIII}{\ensuremath{\text{O~\textsc{iii}}}}
\newcommand{\NII}{\ensuremath{\text{N~\textsc{ii}}}}

\newcommand{\Ha}{\ensuremath{\text{H}\alpha}}
\newcommand{\Hb}{\ensuremath{\text{H}\beta}}

\newcommand{\Msun}{\ensuremath{\text{M}_\odot}}
\newcommand{\kpc}{\ensuremath{\text{kpc}}}
\newcommand{\Mpc}{\ensuremath{\text{Mpc}}}
\newcommand{\Myr}{\ensuremath{\text{Myr}}}
\newcommand{\Gyr}{\ensuremath{\text{Gyr}}}
\newcommand{\kms}{\ensuremath{\text{km}\,\text{s}^{-1}}}
\newcommand{\SFR}{\ensuremath{\text{SFR}}}
\newcommand{\yr}{\ensuremath{\text{yr}}}

@@

\newcommand{\zst}{\ensuremath{z_{\star}}}
\newcommand{\E}[1]{\mathrm{E}[#1]}
\newcommand{\Var}[1]{\mathrm{Var}[#1]}
\newcommand{\Cov}[2]{\mathrm{Cov}[#1,#2]}

@@

\section{Results} \label{sec:results}
\subsection{The transition redshift} \label{ssec:ztran_results}

\begin{figure*}
\includegraphics[width=\textwidth]{plots/aveTb_nf.pdf}
\caption{A summary of the ionization and heating history of our three EoR
models: \hot{}, \fid{}, and \cold{}. \textit{Upper}: the ionization history of
each model, showing that reionization begins ($\avg{x_{\HII}}\sim0.01$) at
$z\sim16$ and ends at $z\sim6$ in each model. In detail the ionization
histories are slightly different, but not drastically. \textit{Lower}: the
heating history of each model, showing the strong differences in the monopole
signal. The transition redshift \zst{} (defined where $P_{21,\delta}(\zst{}) =
0$) for each model is shown as a vertically dashed line. We see that models in
which heating is more efficient have an earlier \zst{}.}
\label{fig:aveTb_nf}
\end{figure*}

\subsection{The halo field}
{\bf If we switch to LIM I think this section should be scrapped, except
showing ztran vs k but using LIM and density instead of halos}
